\documentclass[12pt]{article}
\usepackage[letterpaper, total={7.5in,10in}, centering]{geometry}
\pagenumbering{gobble} % suppresses pagination
\setlength{\parindent}{0pt} % suppressed paragraph indent
\usepackage{multicol} % for contact info
\usepackage{enumitem} % for indented descriptions
\usepackage{setspace} % for doublespacing

\newenvironment{details}{
\begin{itemize}[label={}]
	\small \setlength{\itemsep}{0pt}
}{\end{itemize}}

\begin{document}

\centering \Huge
\textbf{Dominic Ricottone}

\footnotesize
\begin{multicols}{2}
4750 Chevy Chase Dr., Apt. 209 \\
Chevy Chase, Maryland 20815 \\
(716) 548 6305 \\
dominic.ricottone@gmail.com
\end{multicols}

\large
\textbf{Experience} \hrulefill

\normalsize
\textbf{Junior Survey Programmer} at The Harris Poll \hfill \textit{December 2018 -- present}
\begin{details}
 	\item Programming web surveys through the Decipher platform.
\end{details}

\normalsize
\textbf{Junior Data Processing Programmer} at The Harris Poll \hfill \textit{September 2017 --- November 2018}
\begin{details}
 	\item Cleaning and merging survey datasets, and raking data to generate survey weights.
	\item Programming tabulation and typesetting scripts with Quantum to produce client deliverables.
\end{details}

\normalsize
\textbf{Campaign Finance Intern} at Chris Harris \& Associates, LLC \hfill \textit{July 2017 --- September 2017}
\begin{details}
	\item Collecting data on prospective donors, and merging that with in-house donor and voter data.
	\item Administered finances for Todd Baxter, then-Assemblyman Morelle, and late Congresswoman Slaughter.
\end{details}

\normalsize
\textbf{Office Assistant} at Human Resources Dept., U Rochester  \hfill \textit{June 2016 --- May 2017}
\begin{details}
	\item Maintaining primary copies of employment records and databases, including W-2 tax forms and OPM letters.
\end{details}

% \normalsize
% \textbf{Research Assistant} at Cancer Care of Western New York  \hfill \textit{May 2013 --- August 2013}
% \begin{details}
% 	\item Researched the academic literature on penile melanoma for Dr. Roehmholdt's case report.
% \end{details}

\vspace{.2in}
\large
\textbf{Projects} \hrulefill

\small
\begin{flushleft}
	I joined \textbf{the Harris Poll} as it transitioned from the Confirmit survey platform to Decipher. I led the new environment's adoption, with my acheivements including:
\end{flushleft}
\begin{details}
	\item Rewrote XML parsers in our automation tools to handle Decipher's syntax and structures.
%	\item Moved company's codebase from filename-based versioning to a modern Git solution.
	\item Documented Decipher's built-in tabulation solution, and developed the criteria we still use \\
	\hspace{.1in} to determine if it is appropriate for a project.
\end{details}

\small
\begin{flushleft}
	I joined \textbf{Chris Harris \& Associates, LLC} in the lead-up to local elections. My lasting contributions are:
\end{flushleft}
\begin{details}
	\item Wrote PDF- and web-scraping scripts and VBA macros for collecting political contribution data.
	\item Worked with Todd Baxter on his campaign for Monroe County Sheriff. He defeated Patrick O'Flynn, \\
	\hspace{.1in} a $16$-year incumbent, in a $57$-$41$ landslide.
\end{details}

\vspace{.2in}
\large
\textbf{Education} \hrulefill

\normalsize
\textbf{B.A. in Political Science, Economics} from U Rochester \hfill \textit{August 2013 --- May 2017}
\begin{details}
	\item Focuses in \textbf{mathematical modeling} (e.g. Econometrics, Game Theory) and in the \textbf{interaction of \\
	\hspace{.1in} government and the private sector} (e.g. Public Finance, Political Economy, Health Economics).
	\item Cumulative GPA of $3.43$.
\end{details}

\normalsize
\textbf{Intensive Japanese Language Program} at Nanzan University \hfill \textit{January 2016 --- May 2016}
\begin{details}
	\item Immersive study of Japanese language and culture. \\
\end{details}

\vspace{.2in}
\large
\textbf{Technical Skills} \hrulefill

\normalsize
\onehalfspacing
\begin{flushleft}
	Workflow automation---My preferred toolkit is Python, but I've used everything from awk to VBA. \\
	Statistical software and languages including SPSS, STATA, R, SQL, Tableau, and Quantum. \\
	Typesetting languages (i.e., \LaTeX), markup languages (i.e., Markdown, HTML, CSS), and \\
	\hspace{.1in} web programming languages (i.e., JavaScript, jQuery). \\
%	Photo and vector graphics editing with Adobe Photoshop, GIMP, and Inkscape. \\
%	Familiarity with *nix systems, Git workflow, and command-line interfaces.
\end{flushleft}

\footnotesize
\textit{You can find this document and other pieces of my work at at \textbf{https://github.com/dricottone}}

\end{document}
